---
title: "Visualizing SF Crime"
author: "Gaurab Ghosh"
date: "Friday, September 12, 2014"
output: word_document
---

```{r}
library(ggplot2)
crDf = read.csv("sfCrime.csv", header=TRUE, fill=TRUE)
```
Exploratory Data Analysis

```{r}
summary(crDf)
head(crDf)
names(crDf)
nrow(crDf)
```

### WHERE SHOULDN'T YOU PARK YOUR CAR?

```{r}
uniDescription = crDf[!duplicated(crDf["Descript"]),"Descript"]
```

From the uniDescription, we get a sense of the description which tells us where we should not park cars. 
We find the words AUTO and VEHICLE which indicates crimes related to cars. We should target these places not to park cars.

```{r}
toMatch = c("AUTO", "VEHICLE")
add = crDf[grep(paste(toMatch, collapse="|"), crDf[,"Descript"]),c("Address")]
df = as.data.frame(table(add))
df$rank = rank(-df$Freq,ties.method="min")
df = df[order(df$rank,decreasing = F),]
```

Top 10 addresses where most of the AUTO/VEHICLE related thefts have happened:

```{r}
df[1:10,]
```

Bar plot showing the same

```{r}
q = qplot(x=add, y=Freq, data=df[1:10,], geom="bar", stat="identity")
q + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


### WHAT ARE THE SAFEST LOCATIONS IN SF?

```{r}
safeAdd = crDf[,"Address"]
safeDf = as.data.frame(table(safeAdd))
safeDf$rank = rank(-safeDf$Freq,ties.method="min")
safeDf = safeDf[order(safeDf$rank,decreasing = T),]
```

Top 10 Safest Locations in SF:
```{r}
safeDf[1:10,]
```

### WHAT DAY/TIMES ARE ESPECIALLY DANGEROUS?
```{r}
dangerousDay = crDf[,c("DayOfWeek")]
dangDf = as.data.frame(table(dangerousDay))
dangDf$rankDay = rank(-dangDf$Freq, ties.method="min")
dangDf = dangDf[order(dangDf$rank, decreasing=F),]
```

Distribution of Days when crimes have occured:
```{r}
dangDf[1:7,]
q = qplot(x=dangerousDay, y=Freq, data=dangDf, geom="bar", stat="identity")
q + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

